Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-16 doc/GMP2015/s02_preliminaries.tex
Add (k,l)-sparsity matroidal condition in Basics. Slight modification in pinned line incidence to match with Basics.

There exist various results on combinatorial characterization of independence and rigidity
for different types of  rigidity matroid. 
For bar-joint rigidity matroid, 
the famous Laman's theorem~\cite{???} states that the underlying graph
is minimally rigid if and only if $|E| = 2|V|-3$ and $|E'| \le 2|V'|-3$ for every induced subgraph with at least 2 vertices. 
The result by Lovasz and Yemini~\cite{???} shows that all 6-vertex-connected graphs are rigid in the plane. 
For bar-body rigidity matroid,
Tay~\cite{???} proved that
the underlying multigraph is minimally rigid if and only if it can be decomposed as $3$ edge disjoint spanning trees. 
White and Whiteley~\cite{???} gave the same characterization using a different technique to study the algebraic - geomtric conditions called pure condition.
More generally, 
Lee, Streinu and Theran~\cite{???} defined the $(k,l)$-sparsity matroid,
where a hypergraph is called $(k,l)$-sparse if $|E'| \le k|V| - l$ for any induced subgraph with at lease 2 vertices.

>>>>

There are various results on combinatorial characterization of independence and rigidity
for different types of  rigidity matroid. 
For bar-joint rigidity matroid, 
the famous Laman's theorem~\cite{???} states that the underlying graph
is minimally rigid if and only if $|E| = 2|V|-3$ and $|E'| \le 2|V'|-3$ for every induced subgraph with at least 2 vertices. 
The result by Lovasz and Yemini~\cite{???} shows that all 6-vertex-connected graphs are rigid in the plane. 
For bar-body rigidity matroid,
Tay~\cite{???} proved that
the underlying multigraph is minimally rigid if and only if it can be decomposed as $3$ edge disjoint spanning trees. 
White and Whiteley~\cite{???} gave the same characterization using a different technique to study the algebraic - geomtric conditions called pure condition.
More generally, 
Lee, Streinu and Theran~\cite{???} defined the {\em $(k,l)$-sparsity matroid}.
A hypergraph $G$ is called {\em $(k,l)$-sparse} if $|E'| \le k|V'| - l$ for any induced subgraph $(V',E')$ with at least 2 vertices, 
and {\em $(k,l)$-tight} if is $(k,l)$-sparse and $|E| = k|V| - l$. 
In general, if you have a $d$-uniform hypergraph, a $(k,l)$-sparsity
condition is matroidal as long as $l \le dk-1$.

### 2014-12-16 doc/GMP2015/s08_pinnedline.tex
Add (k,l)-sparsity matroidal condition in Basics. Slight modification in pinned line incidence to match with Basics.

The cross-linking  microfibrils can be modeled as a 2-dimensional pinned line incidence constraint system,
where incidence constraints are used instead of distance constraints.

%[2-Dimensional Pinned Line Incidence Graph] \label{prob:pinned_subspace}
A \textbf{2-dimensional pinned line incidence graph}  $G=(V,E, w_V, w_E)$ 
%is a \textbf{2-dimensional pinned line incidence graph},
 has weight functions $w_V(v) = 2, w_E(e) = 1$ for all $v \in V, e \in E$.
Additionally, there is  a  set $X$ of $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$,
such that  %every edge $e \in E$ corresponds to a pin $x \in X$ where
for each edge $e \in E$, there is a uniquely corresponding pin $x \in X$,
such that $e$ is constrained to lie on a line passing through $x$.
%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$

%Let $X$ be a  set of $m$ pins that are fixed in $\mathbb{R}^2$, and $V$ be the index set of a set of vertices.
%For every pin $x \in X$, we are also given the indices of two vertices $v_1,v_2$ in $V$,
%such that the line (edge) spanned by $v_1$ and $v_2$ must pass through $x$.
% % % % % % % % % % % % % % % % % % %
%Find any such set of points $P$ satisfying the given incidences.
%For every pin $x\in X$, we are also given a line $\supp{x}$, %of %a set of $s$-dimensional subspaces passing through
%i.e, a size-two index subset of an unknown set of points $D = \{v_1,\ldots,v_n\}$ in $\mathbb{R}^2$, %$P = \{p_1,\ldots, p_n \}$,
%such that  $x_i$ lies on the line spanned by $\supp{x}$.
%%assume additionally that
%%no $s$ pins lie on any single subspace defined by one of the above hyperedges.
%Find any such set D %$P[X]$
%that satisfies the given subspace incidences. % specified by $\supp[P]{x}$.%$\{S_i\}$. % on $P[X]$ and $X$.

\begin{remark}
For 2-dimensional pinned line incidence graphs,
the constant $k$ used in the definition of independence and rigidity is $0$  \cite{xxx} (see Section~\ref{sec:prelim_defs}).
\end{remark}

In the case of microfibril cross-linking, each fibril is
attached to some fixed larger organelle/membrane at one spot.
Consequently, each fibril can be modeled as an edge of the graph,
with the attachment being the corresponding pin in $X$.
The two cross-linkings on the fibril are modeled as the two vertices in $V$ defining the edge.

Figure~\ref{fig:pinned_line} shows an example of a 2-dimensional pinned line incidence graph,
where the grey ovals stand for pins representing attachments of fibrils,
and the vertices $a_1,a_2,\ldots, d_3$ represent cross-linkings.
% and the black dots stand for vertices/cross-linkings.
%There are  and 10 vertices/cross-linkings in the graph.
The graph is well-constrained, with 12 vertices and 24 edges/pins.

\begin{figure}
  \centering
   \includegraphics[width=.9\linewidth]{img/pinned}
\caption{ A well-constrained 2-dimensional pinned line incidence graph.}
\label{fig:pinned_line}
\end{figure}

@@

In this section, we will adapt the results in Section~\ref{sec:DRP}
to give the Optimal DR-plan for 2-dimensional pinned line incidence graphs.
First, we note the following differences of pinned line incidence graphs from the bar-joint graphs.

@@

\item For pinned line incidence graphs,
since the pins in $X$ have fixed positions on the plane,
o trivial motion exists, therefore {\em no trivial over-constrained graphs exist} (the smallest over-constrained graph has $6$ vertices).\\
In particular, note that both a single vertex and a single edge are under-constrained graphs.

%\todo{Over-constrained trivial subgraphs does not exist??? }\
%\todo{Both a single vertex and a single edge are underconstrained}
%\begin{itemize}
%%\item For  pinned line incidence graphs:
%%no trivial motion exists since the pins have fixed locations.
%\item
%\todo{We just define the %trivial graph/
%DR-plan leaves for 2-dimensional pinned line incidence graphs to be single vertices...  }
%\item \todo{A single edge can be a node of the DR-plan}
%\end{itemize}

\item
For pinned line incidence graphs,
since the pins in $X$ have fixed positions on the plane,
{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
being the disjoint union of two or more well-constrained subgraphs. \\
%Without loss of generality,
%we slightly modify the requirement of DR-plan for pinned line incidence graphs
%such that only connected subgraphs can be considered as a node of the DR-plan.

@@

With the above modification,
we now adapt Theorem~\ref{theorem:main} %, the optimal DR-plan for 2-dimensional bar-joint graphs,
for the optimal DR-plan for 2-dimensional pinned line incidence graphs.

\begin{corollary}
Given a well-constrained 2-dimensional pinned line incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
\begin{enumerate}
    \item if $C_i \cap C_j$ is a single vertex then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$
    \item if $C_i \cap C_j$ is well-constrained then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
\end{enumerate}
\label{cor:pinned}
\end{corollary}

@@

Given Lemma~\ref{lem:pinned_union_intersection} and the modified definition of DR-plan,
proofs of Lemma~\ref{lemma:wc_intersection_is_C} and \ref{corollary:no_edges_between_diff} straightforwardly extend to 2-dimensional pinned line incidence graphs.
The proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for 2-dimensional pinned line incidence graphs 
is given in Appendix~\ref{sec:appendix_pinned}.
The following lemma serves as Lemma~\ref{lemma:uc_intersection_makes_all_uc} for pinned line incidence and can be proved similarly.
\begin{lemma}
\label{lem:vertex_intersection}
If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
\end{lemma}

Given Lemma~\ref{lemma:wc_intersection_makes_all_wc} and Lemma~\ref{lem:vertex_intersection},
it is straightforward to adapt the proof of Theorem~\ref{theorem:main_trivial} and \ref{theorem:main_wellconstrained}
to  2-dimensional pinned line incidence graphs,
thus proving Corollary~\ref{cor:pinned}.
Consequently, we can efficiently find the optimal DR-plan for 2-dimensional pinned line incidence graphs using basically the same algorithm as for 2-dimensional bar-joint graphs.
%we can analyze microfibril cross-linkings by finding the optimal DR-plan for  2-dimensional pinned line incidence graphs in the same way as for 2-dimensional bar-joint graphs.

%TODO ???
The recombination problem for 2-dimensional pinned line incidence systems is trivial.
Since the pins are given fixed positions in the plane,
 the solutions of a well-constrained sub-system will automatically be consistent with solutions of the remaining of the system.

>>>>

The cross-linking  microfibrils can be modeled as a pinned line incidence constraint system in $\mathbb{R}^2$,
where incidence constraints are used instead of distance constraints.

%[2-Dimensional Pinned Line Incidence Graph] \label{prob:pinned_subspace}
A {\em pinned line incidence system} $(G,\delta)$  
is a graph $G=(V,E)$ together with parameters $\delta$ specifying $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$, 
such that each edge is constrained to lie on a line passing through 
the corresponding pin, i.e.\ $\delta: E \rightarrow \mathbb{R}^2$.
%
% $G=(V,E, w_V, w_E)$  
%%is a \textbf{2-dimensional pinned line incidence graph},
% has weight functions $w_V(v) = 2, w_E(e) = 1$ for all $v \in V, e \in E$.
%Additionally, there is  a  set $X$ of $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$,
%such that  %every edge $e \in E$ corresponds to a pin $x \in X$ where
%for each edge $e \in E$, there is a uniquely corresponding pin $x \in X$,
%such that $e$ is constrained to lie on a line passing through $x$.
%%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$
%
A pinned line incidence graph $G$ is rigid if $|E| = 2|V|$ and $|E'| \le 2|V'|$ for every induced subgraph $(V',E')$  \cite{xxx}. 
Note that no trivial motion exists since the pins have fixed positions on the plane.

In the case of microfibril cross-linking, each fibril is
attached to some fixed larger organelle/membrane at one spot.
Consequently, each fibril can be modeled as an edge of the graph,
with the attachment being the corresponding pin.
The two cross-linkings on the fibril are modeled as the two vertices in $V$ defining the edge.

Figure~\ref{fig:pinned_line} shows an example of a  pinned line incidence graph,
where the grey ovals stand for pins representing attachments of fibrils,
and the vertices $a_1,a_2,\ldots, c_3$ represent cross-linkings.
% and the black dots stand for vertices/cross-linkings.
%There are  and 10 vertices/cross-linkings in the graph.
The graph is well-constrained, with 12 vertices and 24 edges/pins.

\begin{figure}
  \centering
   \includegraphics[width=.8\linewidth]{img/pinned}
\caption{ A well-constrained pinned line incidence graph.}
\label{fig:pinned_line}
\end{figure}

@@

In this section, we will adapt the results in Section~\ref{sec:DRP}
to give the Optimal DR-plan for pinned line incidence graphs.
First, we note the following differences of pinned line incidence graphs from the bar-joint graphs.

@@

\item For pinned line incidence graphs,
since the pins have fixed positions on the plane,
no trivial motion exists, therefore {\em no trivial over-constrained graphs exist} (the smallest over-constrained graph has $6$ vertices).\\
In particular, note that both a single vertex and a single edge are under-constrained graphs.

\item
For pinned line incidence graphs,
since the pins have fixed positions on the plane,
{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
being the disjoint union of two or more well-constrained subgraphs. \\
%Without loss of generality,
%we slightly modify the requirement of DR-plan for pinned line incidence graphs
%such that only connected subgraphs can be considered as a node of the DR-plan.

@@

With the above modification,
we now adapt Theorem~\ref{theorem:main} 
for the optimal DR-plan for  pinned line incidence graphs.

\begin{corollary}
Given a well-constrained  pinned line incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
\begin{enumerate}
    \item if $C_i \cap C_j$ is a single vertex then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$
    \item if $C_i \cap C_j$ is well-constrained then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
\end{enumerate}
\label{cor:pinned}
\end{corollary}

@@

Given Lemma~\ref{lem:pinned_union_intersection} and the modified definition of DR-plan,
proofs of Lemma~\ref{lemma:wc_intersection_is_C} and \ref{corollary:no_edges_between_diff} straightforwardly extend to  pinned line incidence graphs.
The proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for pinned line incidence graphs 
is given in Appendix~\ref{sec:appendix_pinned}.
The following lemma serves as Lemma~\ref{lemma:uc_intersection_makes_all_uc} for pinned line incidence and can be proved similarly.
\begin{lemma}
\label{lem:vertex_intersection}
If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
\end{lemma}

Given Lemma~\ref{lemma:wc_intersection_makes_all_wc} and Lemma~\ref{lem:vertex_intersection},
it is straightforward to adapt the proof of Theorem~\ref{theorem:main}
to  pinned line incidence graphs,
thus proving Corollary~\ref{cor:pinned}.
Consequently, we can efficiently find the optimal DR-plan for  pinned line incidence graphs using basically the same algorithm as for  bar-joint graphs.

{\bf Note. }The recombination problem for  pinned line incidence systems is trivial.
Since the pins are given fixed positions in the plane,
 the solutions of a well-constrained sub-system will automatically be consistent with solutions of the remaining of the system.
